Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-04-03 paper/manuscript.Rmd
peaks in may/nov
Update manuscript.Rmd

In total, `r nevents` swimming events occurred throughout the ice-free season,
with a peak in November. On average, caribou swam approximately `r neventidMean`
(range = `r neventidMin`-`r neventidMax`) times per year and remained on each
island for approximately `r dur` (range = `r durMin`-`r durMax`) days before
swimming again. Caribou may swim between islands in the ocean for similar
reasons they swim in freshwater [@Leblond2016]. We propose that one such
explanation, the forage limitation hypothesis, is a likely explanation for
oceanic swimming for caribou that live on islands in the Fogo Island
archipelago.
<!--Is it better
to just state our results here, or give this sort of teaser? Initially I had "86
events by 3 individuals" here, but then we ignore that for a couple paragraphs
of context before getting back into it... which seemed weird
QW: I agree. I've added some Fogo context-->

@@

In total, 12 of 29 collared female caribou swam between islands in the Fogo
Island archipelago. Only `r n10` of these 12 individuals had more than 10
swimming events, suggesting that for ~10% of collared individuals swim
relatively frequently, on average occurring approximately every `r indMean` days
during ice-free seasons. We did not detect any swimming events for the remaining
17 individuals. It remains unclear whether these individuals do not swim, or
whether swimming is rare, and thus undetected, for the majority of individuals
Overall, there appears to be three groups of individuals: those that swim often
(n = 3, every ~`r indMean` days), those that swim occasionally (n = 9, every ~
`r ind2Mean` days), and those that never swam (n = 17). We are also unable to draw
conclusions about the prevalence of swimming in the ocean by male caribou: our
initial visual observation was of an adult male, but our GPS data only included adult
females.

>>>>

In total, `r nevents` swimming events occurred throughout the ice-free season,
with peaks in May and November. On average, caribou swam approximately `r neventidMean`
(range = `r neventidMin`-`r neventidMax`) times per year and remained on each
island for approximately `r dur` (range = `r durMin`-`r durMax`) days before
swimming again. Caribou may swim between islands in the ocean for similar
reasons they swim in freshwater [@Leblond2016]. We propose that one such
explanation, the forage limitation hypothesis, is a likely explanation for
oceanic swimming for caribou that live on islands in the Fogo Island
archipelago.
<!--Is it better
to just state our results here, or give this sort of teaser? Initially I had "86
events by 3 individuals" here, but then we ignore that for a couple paragraphs
of context before getting back into it... which seemed weird
QW: I agree. I've added some Fogo context-->

@@

In total, 12 of 29 collared female caribou swam between islands in the Fogo
Island archipelago. Only `r n10` of these 12 individuals had more than 10
swimming events, suggesting that for ~10% of collared individuals swim
relatively frequently, on average occurring approximately every `r indMean` days
during ice-free seasons. We did not detect any swimming events for the remaining
17 individuals. It remains unclear whether these individuals do not swim, or
whether swimming is rare, and thus undetected, for the majority of individuals.
Overall, there appears to be three groups of individuals: those that swam often
(n = 3, every ~`r indMean` days), those that swam occasionally (n = 9, every ~
`r ind2Mean` days), and those that never swam (n = 17). It is therefore possible that individuals vary in their tendency to swim. We are also unable to draw
conclusions about the prevalence of swimming in the ocean by male caribou: our
initial visual observation was of an adult male, but our GPS data only included adult
females.
